Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-20 papers/clusters.tex
Give fraction of M53 stars in text

The k-means algorithm employed here is by no means optimal, and other clusters
we identify are accompanied by a few stars that are not currently co-spatial.
Those stars may be unassociated interlopers that have been misclassified,
or they may be true cluster members that are now unbound. However in the
case of the high-velocity-dispersion structure in \figurename~\ref{fig:halo},
the situation is far more extreme. We identify a group of stars with
highly similar abundances in 15 dimensions that are now spread throughout
the Galaxy. Because some stars are candidate members of the massive globular
cluster M53, it provides tantalizing possibility that these stars may
indeed be all members of the same co-natal gas cloud, implying that 
these stars have been accreted onto the halo by a single globular
cluster early in the Milky Way's formation. While speculative,
this example demonstrates the promise of chemical tagging.

>>>>

The k-means algorithm employed here is by no means optimal, and other clusters
we identify are accompanied by a few stars that are not currently co-spatial.
Those stars may be unassociated interlopers that have been misclassified,
or they may be true cluster members that are now unbound. However in the
case of the high-velocity-dispersion structure in \figurename~\ref{fig:halo},
the situation is far more extreme. We identify a group of stars with
highly similar abundances in 15 dimensions that are now spread throughout
the Galaxy. Because some stars ($<8\%$) are candidate members of the massive globular
cluster M53, it provides tantalizing possibility that these stars may
indeed be all members of the same co-natal gas cloud, implying that 
these stars have been accreted onto the halo by a single globular
cluster early in the Milky Way's formation. While speculative,
this example demonstrates the promise of chemical tagging.
